Formatting Instructions for NIPS 2015

### 2015-10-06 writing/S'15 LSTM/abstract.tex
Reframing the results.

\begin{abstract} 
Tree-structured neural networks encode a particular tree geometry for a sentence in the network design. However, these models have at best only slightly outperformed simpler sequence-based models. We hypothesize that neural sequence models like LSTMs are in fact able to discover and implicitly use recursive compositional structure, at least for tasks with clear cues to that structure in the data. We demonstrate this possibility using an artificial data task for which recursive compositional structure is crucial, and find that the sequence model can learn the underlying patterning. The sequence model is better in that it learns the value of tree structure from the data in an emergent way, while the tree-structured model is better in being able to learn with greater statistical efficiency due to its informative prior model structure. 
\end{abstract}

>>>>

\begin{abstract} 
Tree-structured neural networks encode a particular tree geometry for a sentence in the network design. However, these models have at best only slightly outperformed simpler sequence-based models. We hypothesize that neural sequence models like LSTMs are in fact able to discover and implicitly use recursive compositional structure, at least for tasks with clear cues to that structure in the data. We demonstrate this possibility using an artificial data task for which recursive compositional structure is crucial, and find an LSTM-based sequence model can learn to exploit the underlying tree structure. However, its performance consistently lags behind that of tree-structured models, even on large training sets, suggesting that tree-structured models retain an advantage in tasks for which it is necessary to exploit recursive structure.
\end{abstract}

### 2015-10-06 writing/S'15 LSTM/intro.tex
Reframing the results.

We compare standard tree and sequence models on their handling of recursive structure by training the models on sentences whose length and recursion depth are limited, and then testing them on longer and more complex sentences, such that only models that exploit the recursive structure will be able to generalize in a way that yields correct interpretations for these test sentences. Our methods are based on those of \newcite{Bowman:Potts:Manning:2014}, who describe an experiment and corresponding artificial dataset which tests this ability in two tree models. We adapt that experiment to sequence models by decorating the statements with an explicit bracketing, and we use this design to compare an LSTM sequence model with three tree models, with a focus on what data each model needs in order to learn the needed generalizations.

As in \newcite{Bowman:Potts:Manning:2014}, we find that standard tree neural networks are able to make the necessary generalizations, with their performance decaying gradually as the structures in the test set grow in size. We additionally find that extending the training set to include larger structures mitigates this decay. Then considering sequence models, we find that a single-layer LSTM is also able to generalize to unseen large structures, but that it does this only when trained on a larger and more complex training set than is needed by the tree models to reach the same generalization performance.

Our results engage with those of \cite{vinyals2014grammar} and \cite{dyer2015transition}, who find that sequence models can learn to recognize syntactic structure in natural language, at least when trained on explicitly syntactic tasks. The simplest model presented in \cite{vinyals2014grammar} uses an LSTM sequence model to encode each sentence as a vector, and then generates a linearized parse (a sequence of brackets and constituent labels) with high accuracy using only the information present in the vector. This shows that the LSTM is able to identify the correct syntactic structures and also hints that it is able to develop a generalizable method for encoding these structures in vectors. However, the massive size of the dataset needed to train the model---250M tokens---leaves open the possibility that it primarily learns to generate only tree structures that it has already seen, representing them as simple hashes---which would not capture unseen tree structures---rather than as structured objects.
Our experiments, though, show that LSTMs can learn to understand tree structures when given enough data, suggesting that there is no fundamental obstacle to learning this kind of structured representation.

>>>>

We compare standard tree and sequence models on their handling of recursive structure by training the models on sentences whose length and recursion depth are limited, and then testing them on longer and more complex sentences, such that only models that exploit the recursive structure will be able to generalize in a way that yields correct interpretations for these test sentences. Our methods are based on those of \cite{Bowman:Potts:Manning:2014}, who describe an experiment and corresponding artificial dataset which tests this ability in two tree models. We adapt that experiment to sequence models by decorating the statements with an explicit bracketing, and we use this design to compare an LSTM sequence model with three tree models, with a focus on what data each model needs in order to learn the needed generalizations.

As in \cite{Bowman:Potts:Manning:2014}, we find that standard tree neural networks are able to make the necessary generalizations, with their performance decaying gradually as the structures in the test set grow in size. We additionally find that extending the training set to include larger structures mitigates this decay. Then considering sequence models, we find that a single-layer LSTM is also able to generalize to unseen large structures, but that it does this only when trained on a larger and more complex training set than is needed by the tree models to reach the same generalization performance.

Our results engage with those of \cite{vinyals2014grammar} and \cite{dyer2015transition}, who find that sequence models can learn to recognize syntactic structure in natural language, at least when trained on explicitly syntactic tasks. The simplest model presented in \cite{vinyals2014grammar} uses an LSTM sequence model to encode each sentence as a vector, and then generates a linearized parse (a sequence of brackets and constituent labels) with high accuracy using only the information present in the vector. This shows that the LSTM is able to identify the correct syntactic structures and also hints that it is able to develop a generalizable method for encoding these structures in vectors. However, the massive size of the dataset needed to train the model---250M tokens---leaves open the possibility that it primarily learns to generate only tree structures that it has already seen, representing them as simple hashes---which would not capture unseen tree structures---rather than as structured objects.
Our experiments, though, show that LSTMs can learn to understand tree structures when given enough data, suggesting that there is no fundamental obstacle to learning this kind of structured representation. We also find, though, that sequence models lag behind tree models across the board, even on training corpora that are quite large relative to the complexity of the underlying grammar, suggesting that tree models can play a valuable role in tasks that require recursive interpretation.
